TR Invariant T.I.

### 2017-04-28 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Getting edge states numerically.

    But now $A$ and $C$ are singular, this makes the
    equation~\ref{eq:rec-disc-eigeneq} mostly undetermined. The simplest case is
    that when $B=0$ (i.e. when $p_x=0$ or $\pm \pi$, and $2-m-\cos(p_x)=0$, thus
    $m=1$ or $3$),
    there are four possible eigenstates of eigenvalue $E=0$:
    \begin{align}
        &\psi_N = \begin{pmatrix}
            1 \\ -1
        \end{pmatrix}\text{ or } \begin{pmatrix}
            0 \\ 0
        \end{pmatrix},\,
        \psi_1 = \begin{pmatrix}
            1 \\ 1
        \end{pmatrix}\text{ or } \begin{pmatrix}
            0 \\ 0
        \end{pmatrix}\nonumber\\
        &\psi_{N-1}=\psi_{N-2} = \cdots = \psi_2 = \begin{pmatrix}
            0 \\ 0
        \end{pmatrix}
    \end{align}
    This shows that it possibly has states localized at the boundary, but this
    tells us nothing when $m$ is not the prescribed values($1$ and $3$).

@@

    Exact value can be found using the formula for solid angle in a
    parameterized surface. Assuming the surface is parameterized as
    \begin{equation}
        \vec{f}(x,y) = (f_1(x,y), f_2(x,y), f_3(x,y))
    \end{equation}
    Its solid angle can be calculated by:
    \begin{equation}
        \int\dd{x}\dd{y} \frac{\vec{f}(x,y)}{\abs{\vec{f}(x,y)}^3}
        \partial_x \vec{f}(x,y) \cross \partial_y \vec{f}(x,y)
    \end{equation}
    This formula can be understood mathematically
    \cite{SolidAngleParameterizedSurface}, and calculated physically (see p.216 of
    \cite{Shen2012}).  The calculated result for different $m$ is plotted in
    fig~\ref{fig:BerryPhase/SSQFormulaPlot}.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.5\linewidth]{pics/BerryPhase/Shape.pdf}
        \caption{Surface formed as $p_x,p_y$ varies}
        \label{fig:BerryPhase/Shape}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/AsMVaries.pdf}
        \caption{As $m$ varies, the shape does not change. The blue plane is the
        $xy$ plane. The center of that surface meets the $xy$-plane when $m=2$.
        That surface leaves the $xy$-plane when $m<0$ or $m>4$.}
        \label{fig:BerryPhase/AsMVaries}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/attempts.pdf}
        \caption{Attempts to determine the Berry phase by dispatching the surface
        into 4 different patches ($m=2$)}
        \label{fig:BerryPhase/attempts}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/SSQFormulaPlot.pdf}
        \caption{Plot of Chern Number for different $m$.}
        \label{fig:BerryPhase/SSQFormulaPlot}
    \end{figure}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

    But now $A$ and $C$ are singular, making the
    equation~\ref{eq:rec-disc-eigeneq} mostly undetermined. The simplest case is
    that when $B=0$ (i.e. when $p_x=0$ or $\pm \pi$, and $2-m-\cos(p_x)=0$, thus
    $m=1$ or $3$), there are four possible eigenstates of eigenvalue $E=0$:
    \begin{align}
        &\psi_N = \begin{pmatrix}
            1 \\ -1
        \end{pmatrix}\text{ or } \begin{pmatrix}
            0 \\ 0
        \end{pmatrix},\,
        \psi_1 = \begin{pmatrix}
            1 \\ 1
        \end{pmatrix}\text{ or } \begin{pmatrix}
            0 \\ 0
        \end{pmatrix}\nonumber\\
        &\psi_{N-1}=\psi_{N-2} = \cdots = \psi_2 = \begin{pmatrix}
            0 \\ 0
        \end{pmatrix}
    \end{align}
    This shows that it possibly has states localized at the boundary, but this
    tells us nothing when $m$ is not the prescribed values($1$ and $3$).

    Numerical calculations can be performed in this case to find eigevectors
    whose eigevectors are close to zero. The result gives real edge states. For
    example, when $N=30$, below are a plot of eigevectors, whose eigenvalues
    $\epsilon$ satisfy $\abs{\epsilon}<0.2$:
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/InfiniteStrip/{InfiniteStrip.N=30.EdgeState}.pdf}
        \caption{Edge states when $N=30$ (amplitudes have not been normalized).}
        \label{fig:InfiniteStrip/InfiniteStrip=30.EdgeState.pdf}
    \end{figure}

@@

    Exact value can be found using the formula for solid angle in a
    parameterized surface. Assuming the surface is parameterized as
    \begin{equation}
        \vec{f}(x,y) = (f_1(x,y), f_2(x,y), f_3(x,y))
    \end{equation}
    Its solid angle can be calculated by:
    \begin{equation}
        \int\dd{x}\dd{y} \frac{\vec{f}(x,y)}{\abs{\vec{f}(x,y)}^3}
        \partial_x \vec{f}(x,y) \cross \partial_y \vec{f}(x,y)
    \end{equation}
    This formula can be understood mathematically
    \cite{SolidAngleParameterizedSurface}, and calculated physically (see p.216 of
    \cite{Shen2012}).  The calculated result for different $m$ is plotted in
    fig~\ref{fig:BerryPhase/SSQFormulaPlot}.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.5\linewidth]{pics/BerryPhase/Shape.pdf}
        \caption{Surface formed as $p_x,p_y$ varies}
        \label{fig:BerryPhase/Shape}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/AsMVaries.pdf}
        \caption{As $m$ varies, the shape does not change. The blue plane is the
        $xy$ plane. The center of that surface meets the $xy$-plane when $m=2$.
        That surface leaves the $xy$-plane when $m<0$ or $m>4$.}
        \label{fig:BerryPhase/AsMVaries}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/attempts.pdf}
        \caption{Attempts to determine the Berry phase by dispatching the surface
        into 4 different patches ($m=2$)}
        \label{fig:BerryPhase/attempts}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/SSQFormulaPlot.pdf}
        \caption{Plot of Chern Number for different $m$.}
        \label{fig:BerryPhase/SSQFormulaPlot}
    \end{figure}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
